### 2019-08-10 paper/paper.tex
Style comments from my earlier commit

\section{Introduction}
When we face a multi-choice question answering (QA) problem where we have to choose the most 
probable answer we arrive at it with prior information and knowledge. for instance, we have some kind of a

Whereas in some cases the state of the art machine-learning methods which were trained on massive amount of data to infer prediction roles
outperforms human-level by a large margin (e.g. SQUAD 2.0 \cite{rajpurkar2018know}),
In the field of common sense reasoning  \cite{talmor2018commonsenseqa} state of the art algorithms fail to generalize and are yet inferior to human level performance.
this is due to two main reasons. first, is that when using algorithms such as fine-tuning a pre-trained language model, it is likely that this knowledge (common sense) does not exist explicitly in the pre training corpus. and second, is due to the fact that creating massive datasets for this purpose solely is hard, and developed only in the last years mostly by crowdsourcing.

Due to this inherent difficulty of this methods the research community invests resources in creating larger-scale datasets in different difficulty levels, e.g., the SWAG \cite{zellers2018swag} dataset with ~100K examples where \cite{devlin2018bert} demonstrate a model which is already at a human level and the CommonseneQA \cite{talmor2018commonsenseqa} a dataset which was made especially for common sense reasoning with \~{}10K samples where the state of the art is much lower then human-level. for a detailed survey of resources see \cite{storks2019commonsense}.

>>>>

\section{Introduction}
When we face a multi-choice question answering (QA) problem where we have to choose the most probable answer, we arrive at it with prior information and knowledge. for instance, we have some kind of a

% TODO: Complete the previous sentence??

While in some cases the state of the art machine-learning methods which were trained on massive amount of data to infer prediction roles
outperforms human-level by a large margin (e.g. SQUAD 2.0 \cite{rajpurkar2018know}),
In the field of common sense reasoning  \cite{talmor2018commonsenseqa} state of the art algorithms fail to generalize and are yet inferior to human level performance.
This is due to two main reasons: first, is that when using algorithms such as fine-tuning a pre-trained language model, it is likely that this knowledge (common sense) does not exist explicitly in the pre training corpus, and second, is due to the fact that creating massive datasets for this purpose solely is hard, and developed only in the last years mostly by crowdsourcing.

Due to this inherent difficulty of this task, the research community invests resources in creating larger-scale datasets with different difficulty levels, e.g., the SWAG \cite{zellers2018swag} dataset with ~100K examples for which \cite{devlin2018bert} demonstrate a model which is already at a human level, and the CommonseneQA \cite{talmor2018commonsenseqa}, a dataset which was made especially for common sense reasoning with \~{}10K samples where the state of the art is much lower then human-level. For a detailed survey of resources see \cite{storks2019commonsense}.
